Transparent Changes

### 2022-04-15 scripts/review.Rmd
Improve review script

# count PubMed results
nrow(pm_data)
# count Web of Science results
nrow(wos_data)
```

@@

# Count removal from missing doi
sum(no_doi)

@@

# Count removal of duplicates
sum(dupl)
```

@@

# Count removal by title filtering
sum(excl)
# count remaining articles
nrow(filtered_data)
```

@@

# Get final decisions
s_res_final <- read.csv("../data/screen/abstract_screening.csv")
# number excluded 
sum(!is.na(s_res_final$decision))
# extract remaining data
ft_screen <- sampled_data[is.na(s_res_final$decision), ]

l <- list.files("../data/fulltext")
get_ft_id <- function(n, files) {
  name <- files[n]
  as.numeric(strsplit(name, "\\.")[[1]][[1]])
}
fts <- purrr::map_dbl(seq_along(l), get_ft_id, files = l)
# find missing full texts
# ft_screen$sid[!ft_screen$sid %in% fts]

@@

>>>>

# count PubMed results
pm_count <- nrow(pm_data)
# count Web of Science results
wos_count <- nrow(wos_data)
overall_count <- pm_count + wos_count
```

The search yielded `r overall_count` results (Pubmed: `r pm_count`; WOS: `r wos_count`)

@@

# Count removal from missing doi
no_doi_count <- sum(no_doi)

@@

# Count removal of duplicates
dupl_count <- sum(dupl)
```

Removed because of missing DOI: `r no_doi_count`
Duplicates removed: `r dupl_count`

Remaining: `r overall_count - no_doi_count - dupl_count`

@@

# Count removal by title filtering
title_excl_count <- sum(excl)
# count remaining articles
forsample_count <- nrow(filtered_data)
```

Removed by automated title filtering: `r title_excl_count`
Remaining articles for random sampling: `r forsample_count`

@@

# Get final decisions
s_res_final <- read.csv("../data/screen/abstract_screening.csv")
# number excluded 
abstr_excl_count <- sum(!is.na(s_res_final$decision))
# extract remaining data
ft_screen <- sampled_data[is.na(s_res_final$decision), ]

@@

Removed by abstract screening: `r abstr_excl_count`

#### Compare full text screening results

```{r fulltext-screening}
# read screening results
f_res_i2 <- read.csv("../data/screen/fulltext_screening_i2.csv")
f_res_i1 <- read.csv("../data/screen/fulltext_screening_i1.csv", sep = ";")

f_res1 <- f_res_i1$fulltext_exclusion
f_res2 <- f_res_i2$fulltext_exclusion

f_res <- purrr::map2_chr(f_res1, f_res2, comp_res)
f_res_df <- data.frame(
  sid = f_res_i2$sid,
  i1 = f_res1,
  i2 = f_res2,
  result = f_res,
  decision = rep.int("", length(f_res1)),
  i1_note = f_res_i1$exclusion_note,
  i2_note = f_res_i2$exclusion_note,
  doi = f_res_i1$doi
)
# write.csv(f_res_df, "../data/screen/fulltext_screening.csv", row.names = FALSE)
# Calculate relative agreement
1 - (sum(f_res == "XXX", na.rm = TRUE) / length(f_res))

1 - ((sum(is.na(f_res1) | is.na(f_res2)) - sum(is.na(f_res))) / length(f_res))

# read final decision
ft_res <- read.csv("../data/screen/fulltext_screening.csv")
ft_res$decision <- factor(
  ft_res$decision, 
  levels = c("t", "l", "r", "h", "m", "c", "e", "d", "o"),
  labels = c("no fulltext", "no english full-text", "no original research", 
             "no humans", "VO2 not measured", "VO2 not continously measured", 
             "no exhaustion", "long protocol", "other")
)
# count exclusions
ft_excl_count <- sum(!is.na(ft_res$decision))

# count remaining articles for data extraction
final_count <- sum(is.na(ft_res$decision))

Excluded after full text screening: `r ft_excl_count`

Remaining articles: `r final_count`

#### Prepare data extraction

```{r extraction, eval=FALSE}
emp <- rep.int("", final_count)

extr <- data.frame(
  sid = ft_res$sid[is.na(ft_res$decision)],
  cart = emp,
  type = emp,
  outcome = emp,
  pre = emp,
  software = emp,
  interpolation = emp,
  ptype = emp,
  averaging = emp,
  parameters = emp,
  source = emp,
  doi = ft_res$doi[is.na(ft_res$decision)]
)

write.csv(extr, "../data/extract/extraction.csv", row.names = FALSE)```
